HiC Contact Map Comaprison Using Graphlet Approach

### 2018-10-16 papers/manuscripts/manuscript.tex
save

\documentclass[a4,center,fleqn]{NAR}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[super]{nth}
\usepackage{multirow}
% Enter dates of publication
\copyrightyear{2017}
\pubdate{18 March 2017}
\pubyear{2017}
\jvolume{37}
\jissue{12}

@@

%\articlesubtype{This is the article type (optional)}

\begin{document}
\title{HiC Contact Map Comaprison Using Graphlet Approach}

\author{%
    Behnam Rasoolian\,$^{1,*}$,
    Debswapna Bhattacharya\,$^{1}$
    \footnote{
    Tel: +1 334 5212814; Email: bzr0014@auburn.edu}}

    \address{%
        $^{1}$ Auburn University
        }
        % Affiliation must include:
        % Department name, institution name, full road and district address,
        % state, Zip or postal code, country

%        \history{%
%            Received January 1, 2009;
%            Revised February 1, 2009;
%            Accepted March 1, 2009}

@@

Recently, Hi-C data has been mostly used to predict
the 3D structure at the chromosome level by satisfying
intra-chromosomal interactions or even at the
full genome by leveraging both inter- and intra-chromosomal
interactions
\cite{noble2011three, 
rousseau2011three, 
hu2013bayesian, 
varoquaux2014statistical, 
trieu2014large, 
zhang20133d, 
lesne20143d, 
bau2011three, 
adhikari2016chromosome3d}.
These efforts, although different in
approach, usually translate interaction frequencies in
contact maps as simple inverse measures of distance.
They then try to find the coordinates of the chromosomal
loci that would result in that particular distance
matrix using optimization. These methods vary in
the optimization models and methodologies used.
Also, efforts has been made recently to learn the
inverse conversion parameters from contact maps
to distance matrices \cite{oluwadare2018maximum}.
The reconstructed 3D structures could be used in
order to compare normal and malignant cell lines.
However, the main obstacle to doing so is that
the process of reconstruction is computationally expensive.
Almost all reconstruction methods rely on either
deterministic or heuristic optimization approaches in
order to find the best conformation that matches contact
maps. Also, there is no experimental way of evaluating
the accuracy of the reconstructed 3D conformations.
One experimental way of partially validating correctness
of reconstruction process is Fluorescence in
situ hybridizaiton (FISH) method. However, this
technique is limited to a few loci and cannot be
extended to cover the whole structure of the chromosomes.
Furthermore, the process of reconstructing 3D
chromatic structure is computationally expensive,
hindering their applicability at the genome-wide scale.
% **************************************************************
% Keep this command to avoid text of first page running into the
% first page footnotes
\enlargethispage{-65.1pt}
% **************************************************************

@@

\subsection{Graphlets and Orbits}
\begin{figure}[H]
    \centering
    \includegraphics[width=.5\textwidth]{figures/graphlets.jpg}
    %\includegraphics[width=.5\textwidth]{/home/bzr0014/Dropbox/graphlets.png}
    %\includegraphics[width=.5\textwidth]{/home/bzr0014/Dropbox/graphlets.jpg}
    \caption{}
    \label{fig_graphlets}
\end{figure}
Recently, graphlet comparison has emerged as
a novel method for comparing large networks in
order to find local similarities in them. A
graph G is a pair $(V,E)$, where $V$ is a set of
vertices and $E \subseteq V\times V$ is a set of
edges. A connected graph is one where there is
a path between every pair of vertices.
Given a graph $G(V, E)$ and $S \subseteq V$,
then $G'(S, E')$ is a graphlet if and only if
it is connected $E' = \{(u, v) | u, v \in V \quad \&
\quad (u, v) \in E \rightarrow (u, v) \in E'\}$. 
There a total of 30 graphlets
of size 2, 3, and 5.  Figure \ref{fig_graphlets}
demonstrates these graphlets. 
As can be seen there is only one graphlet
of size 2 which is equivalent to an edge; that
is, the number of graphlet 1 in a graph is the
same as the number of edges on the graph. There
are also a total of 2 graphlets of size 2, 6
of size 4 and 20 of size 5. The nodes of each graphlet
can be partitioned into sets of topographically equivalent
nodes called orbits. For  example, in  Figure 
\ref{fig_graphlets}, we can see that G3 can be
partitioned into 2 sets of nodes, the middle ones
(white) and the outer nodes (black). 
For the same set of graphlets,
there are 73 orbits that are also illustrated in
figure  Figure using nodes of difference shades.

@@

Instead, in order to threshold the matrix so that both global and local patterns are
captured, we borrowed the concept of \textit{adaptive thresholding} from image 
processing context. In this method, in order to be set, a pixel should have
an intensity larger than the average of non-zero intensities in its
\textit{neighborhood}. The neighborhood is defined by a sliding kernel 
that passes through the contact map with the pixel at its middle at 
each step. Figure \ref{local_thresholded_chr1_chr1} demonstrates result of 
this thresholding approach for intra-chromosomal contact maps of chromosome 1.
Refer to supplementary material for all 23 interchromosomal thresholding
results.
\begin{figure}[t]
    \centering
    \includegraphics[width=.47\textwidth]{figures/local_thresholded_chr1_chr1.png}
    \caption{Result of thresholding interchromosomal contact map of chromosome 1
    using a kernels of size $5 \times 5$ for all cell lines. 
    The first row shows the thresholded
    maps. Second and third rows demonstrate pair-wise similarities and 
    differences between contact maps respectively.}
    \label{local_thresholded_chr1_chr1}
\end{figure}

\subsection{Orbit Extraction}
Once the thresholded contact maps are obtained, graphlets and orbits can be 
extracted. We used the \texttt{orca} package in \texttt{R} programming 
language to extract the graphlets. As a result of graphlet extraction, 
For each loci in each contact map, a \textit{signature vector} of size
73 is created. Thus for each cell line, we would have 276 
\textit{signature matrices} of
size $|V^{ij}|\times 73$, where $V^{ij}$ is the number of loci
involved in contact map between chromosomes $i$ and $j$. Figure
\ref{fig:graphlet_extraction} illustrates the process and results
of signature matrix extraction schematically.
\begin{figure}
    \centering
    \includegraphics[width=.47\textwidth]{figures/graphlet_extraction.png}
    \caption{Graphlet extraction for the four cell lines. For each
    loci in each contact map between chromosomes $i$ and $j$, 
    the signature vectors of length 73 are extracted, resulting 
    in a \textit{signature matrix} of size $|V^{ij}| \times 73$,
    where $V^{ij}$ 
    is the number of loci involved.}
    \label{fig:graphlet_extraction}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figures/graphlet_distance_schema.png}
    \caption{Calculating pair-wise loci distances. For each loci (row) 
    in each
    contact map in MIT cell line, its distance is calculated based on
    equation \ref{eq:distance_total} with the corresponding loci in
    leukemic cells. The result of this process is a 
    \textit{signature distance vector} of size
    $|V^{ij}| = N_i+N_j$ for each contact map.
    }
    \label{graphlet_distance_schema}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figures/graphlet_correlation_schema.png}
    \caption{Calulating pair-wise orbit correlations. For each orbit (column)
    in each contact map in MIT cell line, its correlation with the
    same orbit in the same contact map 
    in leukemic cells is calculated. The result of
    this process is a \textit{signature correlation} vector of size
    73 which captures how similar frequencies of two orbits are.}
    \label{graphlet_correlation_schema}
\end{figure}
%$
%\begin{pmatrix}
%    {S}^A_{\scriptscriptstyle i,j,1,1}         &
%    \cdots                                     &    
%    {S}^A_{\scriptscriptstyle i,j,1,72}        \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \vdots                                     &                
%                                               &      
%    \vdots                                     \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   {S}^A_{\scriptscriptstyle i,j,N_1,1}    &
%   \ddots                                            &    
%   {S}^A_{\scriptscriptstyle i,j,N_1, 72} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \vdots                                     &                
%                                               &      
%    \vdots                                     \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   {S}^A_{\scriptscriptstyle i,j,N_1+N_2,1}   &
%    \cdots                                &
%   {S}^A_{\scriptscriptstyle i,j,N_1+N_2, 72}
%\end{pmatrix}
%$
%
%$
%\begin{pmatrix}
%    {C}^A_{\scriptscriptstyle i,j,1,1}     &
%    \cdots    &
%    {C}^A_{\scriptscriptstyle i,j,1,N_1} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \vdots                             &
%    \ddots&
%    \vdots                             \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    {C}^A_{\scriptscriptstyle i,j,N_1,1}   &
%    \cdots&                  
%    S^A_{\scriptscriptstyle i,j,N_1, N_1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\end{pmatrix}
%$

@@

\section{results and discussions}
\subsection{Contact Map Orbit Vector Distance}
\begin{figure}
    \centering
    \begin{subfigure}[b]{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/orbit_distances_normal_vs_cancer.png}
        \caption{}
        \label{fig:orbit_distances_all_a}
    \end{subfigure}

    \begin{subfigure}[b]{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/orbit_distances_cells.png}
        \caption{}
        \label{fig:orbit_distances_all_b}
    \end{subfigure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/orbit-distances_chr14.png}
    \end{subfigure}
    \caption{   
        Pair-wise graphlet signature distances for all contact maps of
        chromosome 14. Warm colors as used for cancer-cancer pairs and
        cold colors are used for normal-cancer pairs. As can be seen
        cancer-cancer pairs tend to be close to each other than to the
        normal cell. This is specially true for the first 13 
        inter-chromosomal contact maps.
     }
    \label{fig:orbit_distances_chr14}
\end{figure}

@@

\begin{figure*}
    \centering
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_cancer_vs_normal.png}
%    \caption{}
%    \label{fig:contact_map_correlations_all}
%    \end{subfigure}

    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{figures/orbits_correlations_cancer_vs_normal.png}
    \caption{}
    \label{fig:orbits_correlations_normal_vs_cancer}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{figures/orbits_correlations_all.png}
    \caption{}
    \label{fig:orbits_correlations_all}
    \end{subfigure}
    \caption{
        \textbf{Pair-wise 
        average contact map orbit correlations
        for all contact maps:}
        ($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j} 
        \quad \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$:
        average along the 
        red \textit{vertical} arrow in figure 
        \ref{graphlet_correlation_schema}).
        These values are calculated by averaging over 
        pairwise correlations of orbits of
        $\mathbb{Q}$ in a contact map.
        \textbf{Pair-wise average orbit correlations:}
        In figure \ref{fig:orbits_correlations_all}, each point
        in the graph is the result of averaging pair-wise
        orbit correlations over all contact maps
        ($\frac{1}{276}\sum_{i=0}^{23}\sum_{j=i}^{23}{
        m^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j, o}} \quad 
        \forall o \in \{0, 1, ..., 72\}$:
        average along the red \textit{horizontal} arrows in figure 
        \ref{graphlet_correlation_schema}).
        Counts for certain orbits are always zero in inter-chromosomal
        maps, leading to average value close to zero in 
        Figure \ref{fig:orbits_correlations_all}.
        In this figure, cancer cells data points are depicted
        in warm colors while normal cells are depicted in
        cold colors in increased contrast. As can be seen
        orbit distributions are more similar to each other
        for cancer cells.
    }
    \label{fig:orbits_correlations}
\end{figure*}

@@

\bibliography{lit}
\bibliographystyle{unsrt}
\end{document}

>>>>

\documentclass[]{article}
\usepackage[top=1in, bottom=1.25in, left=1in, right=1in]{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[super]{nth}
\usepackage{multirow}
% Enter dates of publication
%\copyrightyear{2017}
%\pubdate{18 March 2017}
%\pubyear{2017}
%\jvolume{37}
%\jissue{12}

@@

%\articlesubtype{This is the article type (optional)}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}

\title{HiC Contact Map Comaprison Using Graphlet Approach}
\author[1]{Behnam Rasoolian \thanks{Tel: +1 334 5212814; Email: bzr0014@auburn.edu}}
\author[1]{Debswapna Bhattacharya}
\affil[1]{Department of Computer Science and Software Engineering, Auburn University}
\date{}
\renewcommand\Authands{ and }

\begin{document}

@@

Recently, Hi-C data has been mostly used to predict
the 3D structure at the chromosome level by satisfying
intra-chromosomal interactions or even at the
full genome by leveraging both inter- and intra-chromosomal
interactions
\cite{noble2011three, 
rousseau2011three, 
hu2013bayesian, 
varoquaux2014statistical, 
trieu2014large, 
zhang20133d, 
lesne20143d, 
bau2011three, 
adhikari2016chromosome3d}.
These efforts, although different in
approach, usually translate interaction frequencies in
contact maps as simple inverse measures of distance.
They then try to find the coordinates of the chromosomal
loci that would result in that particular distance
matrix using optimization. These methods vary in
the optimization models and methodologies used.
Also, efforts has been made recently to learn the
inverse conversion parameters from contact maps
to distance matrices \cite{oluwadare2018maximum}.
The reconstructed 3D structures could be used in
order to compare normal and malignant cell lines.
However, the main obstacle to doing so is that
the process of reconstruction is computationally expensive.
Almost all reconstruction methods rely on either
deterministic or heuristic optimization approaches in
order to find the best conformation that matches contact
maps. Also, there is no experimental way of evaluating
the accuracy of the reconstructed 3D conformations.
One experimental way of partially validating correctness
of reconstruction process is Fluorescence in
situ hybridizaiton (FISH) method. However, this
technique is limited to a few loci and cannot be
extended to cover the whole structure of the chromosomes.
Furthermore, the process of reconstructing 3D
chromatic structure is computationally expensive,
hindering their applicability at the genome-wide scale.
% **************************************************************
% Keep this command to avoid text of first page running into the
% first page footnotes
%\enlargethispage{-65.1pt}
% **************************************************************

@@

\subsection{Graphlets and Orbits}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/graphlets.jpg}
    %\includegraphics[width=.5\textwidth]{/home/bzr0014/Dropbox/graphlets.png}
    %\includegraphics[width=.5\textwidth]{/home/bzr0014/Dropbox/graphlets.jpg}
    \caption{}
    \label{fig_graphlets}
\end{figure}
Recently, graphlet comparison has emerged as
a novel method for comparing large networks in
order to find local similarities in them. A
graph G is a pair $(V,E)$, where $V$ is a set of
vertices and $E \subseteq V\times V$ is a set of
edges. A connected graph is one where there is
a path between every pair of vertices.
Given a graph $G(V, E)$ and $S \subseteq V$,
then $G'(S, E')$ is a graphlet if and only if
it is connected $E' = \{(u, v) | u, v \in V \quad \&
\quad (u, v) \in E \rightarrow (u, v) \in E'\}$. 
There a total of 30 graphlets
of size 2, 3, and 5.  Figure \ref{fig_graphlets}
demonstrates these graphlets. 
As can be seen there is only one graphlet
of size 2 which is equivalent to an edge; that
is, the number of graphlet 1 in a graph is the
same as the number of edges on the graph. There
are also a total of 2 graphlets of size 2, 6
of size 4 and 20 of size 5. The nodes of each graphlet
can be partitioned into sets of topographically equivalent
nodes called orbits. For  example, in  Figure 
\ref{fig_graphlets}, we can see that G3 can be
partitioned into 2 sets of nodes, the middle ones
(white) and the outer nodes (black). 
For the same set of graphlets,
there are 73 orbits that are also illustrated in
figure  Figure using nodes of difference shades.

@@

Instead, in order to threshold the matrix so that both global and local patterns are
captured, we borrowed the concept of \textit{adaptive thresholding} from image 
processing context. In this method, in order to be set, a pixel should have
an intensity larger than the average of non-zero intensities in its
\textit{neighborhood}. The neighborhood is defined by a sliding kernel 
that passes through the contact map with the pixel at its middle at 
each step. Figure \ref{local_thresholded_chr1_chr1} demonstrates result of 
this thresholding approach for intra-chromosomal contact maps of chromosome 1.
Refer to supplementary material for all 23 interchromosomal thresholding
results.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/local_thresholded_chr1_chr1.png}
    \caption{Result of thresholding interchromosomal contact map of chromosome 1
    using a kernels of size $5 \times 5$ for all cell lines. 
    The first row shows the thresholded
    maps. Second and third rows demonstrate pair-wise similarities and 
    differences between contact maps respectively.}
    \label{local_thresholded_chr1_chr1}
\end{figure}

\subsection{Orbit Extraction}
Once the thresholded contact maps are obtained, graphlets and orbits can be 
extracted. We used the \texttt{orca} package in \texttt{R} programming 
language to extract the graphlets. As a result of graphlet extraction, 
For each loci in each contact map, a \textit{signature vector} of size
73 is created. Thus for each cell line, we would have 276 
\textit{signature matrices} of
size $|V^{ij}|\times 73$, where $V^{ij}$ is the number of loci
involved in contact map between chromosomes $i$ and $j$. Figure
\ref{fig:graphlet_extraction} illustrates the process and results
of signature matrix extraction schematically.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/graphlet_extraction.png}
    \caption{Graphlet extraction for the four cell lines. For each
    loci in each contact map between chromosomes $i$ and $j$, 
    the signature vectors of length 73 are extracted, resulting 
    in a \textit{signature matrix} of size $|V^{ij}| \times 73$,
    where $V^{ij}$ 
    is the number of loci involved.}
    \label{fig:graphlet_extraction}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/graphlet_distance_schema.png}
    \caption{Calculating pair-wise loci distances. For each loci (row) 
    in each
    contact map in MIT cell line, its distance is calculated based on
    equation \ref{eq:distance_total} with the corresponding loci in
    leukemic cells. The result of this process is a 
    \textit{signature distance vector} of size
    $|V^{ij}| = N_i+N_j$ for each contact map.
    }
    \label{graphlet_distance_schema}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/graphlet_correlation_schema.png}
    \caption{Calulating pair-wise orbit correlations. For each orbit (column)
    in each contact map in MIT cell line, its correlation with the
    same orbit in the same contact map 
    in leukemic cells is calculated. The result of
    this process is a \textit{signature correlation} vector of size
    73 which captures how similar frequencies of two orbits are.}
    \label{graphlet_correlation_schema}
\end{figure}
%$
%\begin{pmatrix}
%    {S}^A_{\scriptscriptstyle i,j,1,1}         &
%    \cdots                                     &    
%    {S}^A_{\scriptscriptstyle i,j,1,72}        \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \vdots                                     &                
%                                               &      
%    \vdots                                     \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   {S}^A_{\scriptscriptstyle i,j,N_1,1}    &
%   \ddots                                            &    
%   {S}^A_{\scriptscriptstyle i,j,N_1, 72} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \vdots                                     &                
%                                               &      
%    \vdots                                     \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   {S}^A_{\scriptscriptstyle i,j,N_1+N_2,1}   &
%    \cdots                                &
%   {S}^A_{\scriptscriptstyle i,j,N_1+N_2, 72}
%\end{pmatrix}
%$
%
%$
%\begin{pmatrix}
%    {C}^A_{\scriptscriptstyle i,j,1,1}     &
%    \cdots    &
%    {C}^A_{\scriptscriptstyle i,j,1,N_1} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \vdots                             &
%    \ddots&
%    \vdots                             \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    {C}^A_{\scriptscriptstyle i,j,N_1,1}   &
%    \cdots&                  
%    S^A_{\scriptscriptstyle i,j,N_1, N_1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\end{pmatrix}
%$

@@

\section{results and discussions}
\subsection{Contact Map Orbit Vector Distance}
\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{figures/orbit_distances_normal_vs_cancer.png}
        \caption{}
        \label{fig:orbit_distances_all_a}
    \end{subfigure}

    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{figures/orbit_distances_cells.png}
        \caption{}
        \label{fig:orbit_distances_all_b}
    \end{subfigure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{figures/orbit-distances_chr14.png}
    \end{subfigure}
    \caption{   
        Pair-wise graphlet signature distances for all contact maps of
        chromosome 14. Warm colors as used for cancer-cancer pairs and
        cold colors are used for normal-cancer pairs. As can be seen
        cancer-cancer pairs tend to be close to each other than to the
        normal cell. This is specially true for the first 13 
        inter-chromosomal contact maps.
     }
    \label{fig:orbit_distances_chr14}
\end{figure}

@@

\begin{figure}
    \centering
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_cancer_vs_normal.png}
%    \caption{}
%    \label{fig:contact_map_correlations_all}
%    \end{subfigure}

    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{figures/orbits_correlations_cancer_vs_normal.png}
    \caption{}
    \label{fig:orbits_correlations_normal_vs_cancer}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{figures/orbits_correlations_all.png}
    \caption{}
    \label{fig:orbits_correlations_all}
    \end{subfigure}
    \caption{
        \textbf{Pair-wise 
        average contact map orbit correlations
        for all contact maps:}
        ($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j} 
        \quad \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$:
        average along the 
        red \textit{vertical} arrow in figure 
        \ref{graphlet_correlation_schema}).
        These values are calculated by averaging over 
        pairwise correlations of orbits of
        $\mathbb{Q}$ in a contact map.
        \textbf{Pair-wise average orbit correlations:}
        In figure \ref{fig:orbits_correlations_all}, each point
        in the graph is the result of averaging pair-wise
        orbit correlations over all contact maps
        ($\frac{1}{276}\sum_{i=0}^{23}\sum_{j=i}^{23}{
        m^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j, o}} \quad 
        \forall o \in \{0, 1, ..., 72\}$:
        average along the red \textit{horizontal} arrows in figure 
        \ref{graphlet_correlation_schema}).
        Counts for certain orbits are always zero in inter-chromosomal
        maps, leading to average value close to zero in 
        Figure \ref{fig:orbits_correlations_all}.
        In this figure, cancer cells data points are depicted
        in warm colors while normal cells are depicted in
        cold colors in increased contrast. As can be seen
        orbit distributions are more similar to each other
        for cancer cells.
    }
    \label{fig:orbits_correlations}
\end{figure}

@@

\bibliography{lit}
\bibliographystyle{unsrt}

\end{document}
